Artin Group Presentations Arising from Cluster Algebras

### 2014-08-01 Paper.tex
"Put in Charney to paper"

\begin{lem} \cite[Lemma 2.4]{BM13}
Suppose that a vertex k is connected to at least one vertex of a chordless cycle in a diagram $\Gamma$ of finite type. Then k is connected to at most two vertices in the cycle, and if it is connected to two vertices, they must be adjacent in the cycle.
\end{lem}

@@

\end{note}
\begin{defn}
\cite[Beginning of section 1.2]{artin} \todo{put reference for artin, found at the bottom, in bibliography, but I don't know how to use this bibliography format. - it's just BibTex, which you'll almost certainly want to learn at some point.  Try editing References.bib, and if you have trouble feel free to ask me for help - David}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

@@

artin: http://people.brandeis.edu/~charney/papers/RAAGfinal.pdf

>>>>

%\begin{lem} \cite[Lemma 2.4]{BM13}
%Suppose that a vertex k is connected to at least one vertex of a chordless cycle in a diagram $\Gamma$ of finite type. Then k is connected to at most two vertices in the cycle, and if it is connected to two vertices, %they must be adjacent in the cycle.
%\end{lem}

@@

\end{note}
\begin{defn}
\cite[Beginning of section 1.2]{C06}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

@@
